What do incoming university students believe about open science practices in

### 2021-03-09 analysis/Manuscript.Rmd
Drafting method section
Added the three measures to the Method section

>>>>

### Open Science Norms and Counternorms

Our approach to measuring norms and counternorms focussed on participants' evaluation of ten specific open science practices that reflected open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf. Anderson et al., 2007). 
The open science practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficent information of replicability, preprints, open materials, open data, and open access publishing. Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." There were 20 scenarios in total.
For example, the practice of posting article preprints was evaluated with the pro-open science item, "Deborah should post a manuscript describing the Findings of her study openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal." The counter-open preprint item read, "Deborah should not post a manuscript describing the findings of her study online until after it has been checked by experts (peer reviewed) and accepted for publication in a journal." Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.

### Norms in Practice

We also sought to measure participants' normative beliefs about how psychological science was actually conducted by researchers around the world. To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" The ten characteristics explicitly described each of the ten open science practices named above. For example, "A manuscript describing the findings of the study is posted openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal." Participants were given a slider bar ranging from 0% to 100% to record their estimate.

### Beliefs About Replications

Participants' beliefs about the replicabilty of results in psychological science were indexed by two questions. The first asked participants to "Imagine that a set of researchers selected 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants. We call repeating a study like this a “replication study”. At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?” Estimates were recorded using a slider bar ranging from 0% to 100%. The second question asked participants whether they had heard of the replication crisis. For those who said they had, two open-ended
